Ensuring Fairness with Transparent Auditing of Quantitative Bias in AI Systems

### 2024-08-18 slides/2024_8_30.tex
Fixed typo

\begin{frame}[fragile]
    \frametitle{Application}
    \begin{align*}
        \priv(r_i) & := r_i(\text{``race''}) \neq \text{``African-American''}\\
        \pos(r_i)  & := r_i(\text{``score\_text''}) \in \set{\text{``Medium''},\text{``High''}}\\
        \tru(r_i)  & := r_i(\text{``two\_year\_recid''}) == \text{True}
    \end{align*}
    These predicates can then be encoded with Python functions:
    \begin{center}
    \begin{minipage}{0.8\textwidth}
    \begin{minted}[fontsize=\small, frame=single, linenos]{python}
equal_opportunity(
    0.2,
    lambda row: row['race'] == 'African-American',
    lambda row: row['score_text']
      in {'Medium', 'High'},
    lambda row: row['is_recid'] == '1')
    \end{minted}
    \end{minipage}
    \end{center}
\end{frame}

>>>>

\begin{frame}[fragile]
    \frametitle{Application}
    \begin{align*}
        \priv(r_i) & := r_i(\text{``race''}) \neq \text{``African-American''}\\
        \pos(r_i)  & := r_i(\text{``score\_text''}) \in \set{\text{``Medium''},\text{``High''}}\\
        \tru(r_i)  & := r_i(\text{``two\_year\_recid''}) == \text{True}
    \end{align*}
    These predicates can then be encoded with Python functions:
    \begin{center}
    \begin{minipage}{0.8\textwidth}
    \begin{minted}[fontsize=\small, frame=single, linenos]{python}
equal_opportunity(
    0.2,
    lambda row: row['race'] != 'African-American',
    lambda row: row['score_text']
      in {'Medium', 'High'},
    lambda row: row['is_recid'] == '1')
    \end{minted}
    \end{minipage}
    \end{center}
\end{frame}
